---
# No `title:` on purpose -- the default Typst article template centres it.
# The name block below is rendered directly instead.
format:
  typst:
    papersize: us-letter
    margin:
      x: 1.7cm
      y: 1.6cm
    fontsize: 9.5pt
    # Open Sans is the typeface the LaTeX CV used (\usepackage{opensans}) and,
    # unlike Avenir Next, it is installable on Linux -- see fonts-open-sans in
    # .devcontainer/Containerfile and in the CI workflow. Quarto collapses a
    # comma-separated `mainfont` into a single family name rather than a
    # fallback stack, so this must name exactly one installed family.
    mainfont: "Open Sans"
    include-in-header:
      - text: |
          #let accent = rgb("#00707a")
          #let muted  = rgb("#6b7280")

          // 1.5 line spacing, exactly: pin the line box to 1em via the text
          // edges, then a 0.5em gap gives a 1.5em baseline-to-baseline step.
          #set text(top-edge: 0.75em, bottom-edge: -0.25em)
          #set par(justify: false, leading: 0.5em)
          #set block(spacing: 1.05em)
          #show link: set text(fill: accent)

          // Running header from page 2 on: the network mark and the name.
          // No page number here -- the template already numbers pages at the
          // foot, and setting `numbering` back to none would be overridden by
          // the template's own `#set page(...)`, which comes after this block.
          #set page(header: context {
            if counter(page).get().first() > 1 {
              set text(size: 8pt, fill: muted)
              box(baseline: 0.3em, image("fig/ukfaculty.png", width: 0.85cm))
              h(0.4em)
              emph[George G. Vega Yon, Ph.D.]
              v(-0.4em)
              line(length: 100%, stroke: 0.4pt + luma(85%))
            }
          })

          // Section heading: small, spaced caps with a hairline rule.
          #show heading.where(level: 1): it => block(width: 100%, breakable: false, below: 0.85em, above: 1.5em)[
            #text(size: 10pt, weight: "bold", fill: accent, tracking: 0.09em)[
              #upper(it.body)
            ]
            #v(-0.45em)
            #line(length: 100%, stroke: 0.6pt + accent.lighten(55%))
          ]

          // Tighter numbered/bulleted lists for the bibliography sections.
          #set enum(indent: 0pt, body-indent: 0.55em, spacing: 0.72em)
          #set list(indent: 0pt, body-indent: 0.55em, spacing: 0.72em)

          // A titled entry with a right-aligned date.
          #let dated(title, date, ..rest) = block(below: 0.75em, breakable: false)[
            #grid(columns: (1fr, auto), column-gutter: 1em,
              text(weight: "bold")[#title],
              text(fill: muted, size: 9pt)[#date])
            #for r in rest.pos() [ #text(size: 9pt)[#r] \ ]
          ]

          // A one-line item with a right-aligned date (awards, books).
          #let oneline(body, date) = block(below: 0.5em)[
            #grid(columns: (1fr, auto), column-gutter: 1em,
              body, text(fill: muted, size: 9pt)[#date])
          ]

          // CRAN download badge, emitted inline by R/downloads.R.
          #let dlbadge(n) = box(
            baseline: 0.15em,
            fill: accent.lighten(88%),
            inset: (x: 0.42em, y: 0.22em),
            radius: 2.5pt,
            text(size: 7pt, fill: accent.darken(12%), weight: "medium")[↓ #n]
          )
execute:
  echo: false
  warning: false
knitr:
  opts_chunk:
    # The default SVG device needs cairo/X11, which isn't present here; this
    # document has no figures, so a plain PNG device is enough.
    dev: png
---

```{r}
#| include: false
source("R/bib.R")
source("R/downloads.R")

bibs <- c("../papers.bib", "../software.bib",
          "../presentations-conference.bib", "../presentations-invited.bib",
          "../presentations-other.bib")
assert_no_accent_macros(bibs)          # accents must be literal UTF-8

pubs   <- read_bibs(bibs[1])
soft   <- read_bibs(bibs[2])
talks  <- read_bibs(bibs[3], bibs[4], bibs[5])
counts <- read_downloads()             # cached; `make downloads` to refresh
```

```{=typst}
// The network sits top-right, out of the text flow, like the LaTeX original.
// Raised so it clears the contact line, which runs close to the right margin.
#place(top + right, dy: -1.1cm, image("fig/ukfaculty.png", width: 5cm))

#block(below: 1.5em)[
  #text(size: 20pt, weight: "bold")[George G. Vega Yon, Ph.D.]
  #v(0.15em)
  #text(size: 9.5pt, fill: muted)[
    Research Associate Professor, Division of Epidemiology, University of Utah
  ]
  #v(0.35em)
  #text(size: 9pt)[
    #link("mailto:g.vegayon@gmail.com")[g.vegayon\@gmail.com]
    #h(0.5em) · #h(0.5em) #link("https://ggvy.cl")[ggvy.cl]
    #h(0.5em) · #h(0.5em) #link("https://github.com/gvegayon")[github.com/gvegayon]
    #h(0.5em) · #h(0.5em) #link("https://orcid.org/0000-0002-3171-0844")[orcid.org/0000-0002-3171-0844]
  ]
]
```

# Major Areas of Research Interest

Social Networks and Complex Systems · Statistical Computing · Scientific
Software Development · Mechanistic Machine Learning · Statistical Methods
Development

# Education

```{=typst}
#dated[Ph.D. in Biostatistics (concentration in Statistical Computing)][2020][University of Southern California, USA][
  Dissertation: _Essays on Bioinformatics and Social Network Analysis: Statistical and Computational Methods for Complex Systems._]
#dated[M.Sc. in Social Sciences (concentration in Economics)][2016][California Institute of Technology, USA]
#dated[Master in Economics and Public Policy][2011][Universidad Adolfo Ibáñez, Chile]
#dated[B.S. in Business Administration (minor in Political Science)][2011][Universidad Adolfo Ibáñez, Chile]
```

# Academic and Professional Experience

```{=typst}
#dated[Research Associate Professor][July 2026 -- Present][Division of Epidemiology, University of Utah]
#dated[Adjunct Assistant Professor][July 2026 -- Present][Kahlert School of Computing, University of Utah]
#dated[Adjunct Assistant Professor][Jan 2023 -- Present][Division of Population Health Sciences, University of Utah]
#dated[Research Assistant Professor][Nov 2021 -- June 2026][Division of Epidemiology, University of Utah]
#dated[Data Scientist (contractor)][May 2024 -- Dec 2025][Center for Forecasting and Outbreaks Analytics, CDC]
#dated[Lead Data Scientist (Associate)][Nov 2023 -- May 2024][Booz Allen Hamilton]
#dated[Research Programmer][Feb 2018 -- Nov 2021][Department of Preventive Medicine, University of Southern California]
#dated[Programmer Analyst][Oct 2015 -- Feb 2018][Department of Preventive Medicine, University of Southern California]
#dated[Graduate Student Researcher][Aug 2011 -- Oct 2015][Division of Social Sciences, California Institute of Technology]
#dated[Analyst][Aug 2011 -- Aug 2014][Research Division, Chilean Pension Supervisor]
#dated[Founding Partner][Jan 2012 -- Jan 2014][Nodos Chile Social Network Analysis Ltda.]
#dated[Adjunct Professor of Statistical Computing][Jan 2011 -- Jun 2012][School of Government, Universidad Adolfo Ibáñez]
```

# Awards

```{=typst}
#oneline[Top paper award, International Communication Association][2022]
#oneline[Travel Grant, Society of Young Network Scientists][2019]
#oneline[Fellowship, California Institute of Technology][2014]
#oneline[Honorable Mention (Posters Session), Chilean Economics Society][2012]
#oneline[Scholarship, Universidad Adolfo Ibáñez][2006]
```

# Peer Reviewed Publications

```{r}
#| results: asis
emit_section(pubs, "published", fmt_pub)
```

# Work in Progress and Technical Reports

```{r}
#| results: asis
emit_section(pubs, "wip", fmt_pub)
```

# Books

```{=typst}
#oneline[_Applied Network Science with R_ (in development). #link("https://book.ggv.cl/")[book.ggv.cl]][]
#oneline[_Applied HPC with R_ (in development). #link("https://book-hpc.ggv.cl/")[book-hpc.ggv.cl]][]
#oneline[_AI for the Scientist in a Hurry_ (in development). #link("https://book-ai.ggv.cl/")[book-ai.ggv.cl]][]
```

# Software Packages

```{r}
#| results: asis
es <- sort_entries(soft)
for (i in seq_along(es)) {
  cat(sprintf("%d. %s%s\n\n", i, fmt_software(es[[i]]),
              dl_badge(pkg_name(es[[i]]), counts)))
}
```

```{r}
#| results: asis
if (length(counts)) cat(sprintf(
  "\n_Badges show total CRAN downloads (%s across %d packages), as of %s._\n",
  format(sum(counts), big.mark = ","), length(counts),
  format(file.mtime("data/downloads.csv"), "%B %Y")))
```

# Grants

```{=typst}
#dated[Quantum-Enhanced Epidemiological Modeling for Public Health Decision-Making][2026 -- 2027][
  University of Utah Seed Grant (PIs: Vega Yon, Basu Roy). Role: Co-PI. Total award: \$50,000.][
  Explores the potential of quantum computing to enhance epidemiological modeling and public
  health decision-making, by implementing a quantum-enhanced version of an epidemiological ABM.]

#dated[Statistical Methods for Integrative Genomics in Cancer][07-01-2016 -- 08-31-2027][
  5P01CA196569-08, National Cancer Institute (PIs: Gauderman, Siegmund). Role: Co-Investigator.
  0.6 calendar months/year. Total award (incl. indirect): \$12,894,663.][
  Develops novel statistical methods for integrating multi-omic data to address cancer etiology,
  prognosis, and treatment. I am Co-I on the project using evolutionary models for annotating genes.]

#dated[Phenotypes of Epilepsy Etiology and Drug Resistance (PEER)][07-01-2023 -- 06-30-2026][
  HT94252310221, U.S. Army Medical Research and Development Command (PI: Kennedy).
  Role: Co-Investigator. 1.8 calendar months/year. Total award (incl. indirect): \$846,484.][
  Investigates the causes and mechanisms of epilepsy using new data science methods, generating
  risk scores for epilepsy after head injury among military personnel.]

#dated[TRANSMIT: Training Research Acumen in Students Modeling Infectious Threats][09-30-2022 -- 09-29-2025][
  5U01CK000675-01, National Center for Emerging and Zoonotic Infectious Diseases (PI: Keegan).
  Role: Co-Investigator. 0.3 calendar months/year. Total award (incl. indirect): \$891,356.][
  A fellowship program training students in mathematical modeling and computational methods
  for the study of infectious diseases.]

#v(0.4em)
#text(style: "italic", fill: muted)[Submitted but not funded]
#v(0.4em)

#dated[Improving our Predictive Capability of Gene Functions by Leveraging Biological Insights with Advanced Statistical Computing][12-01-2022 -- 11-30-2027][
  1R01HG012878-01, National Human Genome Research Institute (PI: Vega Yon). Role: PI.][
  Uses discrete exponential-family models to build a mechanistic gene function evolution model
  incorporating biological processes such as neofunctionalization.]

#dated[Building a Novel Prediction Framework Leveraging Biological Insights to Boost Machine Learning Algorithms for Annotating Gene Function][12-01-2023 -- 11-30-2028][
  1R01HG012878-01A1, National Human Genome Research Institute (PI: Vega Yon). Role: PI.][
  Extends the model of function evolution using discrete exponential-family models, embedding it
  into a mechanistic machine learning framework.]
```

# Teaching

```{=typst}
#dated[(PHS 7045) Advanced Programming with R and HPC][Fall 2024][The University of Utah, USA][Co-instructor, PHS Ph.D. Program]
#dated[(PHS 7045) Advanced Programming with R and HPC][Fall 2022][The University of Utah, USA][Co-instructor, PHS Ph.D. Program]
#dated[(PM 566) Introduction to Health Data Science][Fall 2021][University of Southern California, USA][Instructor, M.Sc. in Public Health Data Science]
#dated[(PM 566) Introduction to Health Data Science][Fall 2020][University of Southern California, USA][Co-instructor, M.Sc. in Public Health Data Science]
#dated[Statistical Computing with Stata][2012][Universidad Adolfo Ibáñez, Chile][Instructor, Masters in Economics and Public Policy]
#dated[Microeconomics][2012][Universidad Adolfo Ibáñez, Chile][Co-instructor, B.A. in Business Administration]
#dated[Introduction to Economics][2011--2012][Universidad Adolfo Ibáñez, Chile][Co-instructor, B.A. in Business Administration]
```

# Mentoring and Advising

```{=typst}
#dated[Sima Najafzadehkhoei --- Mentor, RA][2024 -- Present][
  University of Utah, Population Health Sciences, Ph.D. in Biostatistics.
  Computational epidemiology, agent-based models and ML.]
#dated[Anibal Olivera --- Mentor, RA][2024 -- Present][
  Universidad del Desarrollo, Chile, Ph.D. in Social Complexity. Network science and R package development.]
#dated[Olivia Banks --- Mentor, RA][2024 -- Present][
  University of Utah, undergraduate double major in Computer Science and Cellular and Molecular Biology.
  Software development and computational epidemiology.]
#dated[Eric Anto --- Ph.D. Dissertation Committee Member][2023 -- Present][
  University of Utah, Population Health Sciences, Biostatistics Ph.D. program.]
#dated[Hyrum Thomas Diesen --- Mentor, RA][2024 -- 2025][
  University of Utah, School of Biological Sciences, Molecular Cellular Evolutionary Biology Ph.D. program.]
#dated[Katherine Lawson Michod --- Qualifying Exam Chair and Dissertation Committee Member][2022 -- 2024][
  University of Utah, Population Health Sciences, Clinical and Translational Epidemiology Ph.D. program.]
#dated[Derek Meyer --- Supervisor, RA, and M.Sc. Dissertation Committee Member][2022 -- 2024][
  University of Utah, Population Health Sciences. Agent-based models for epidemics.]
#dated[Jacqueline M. Kent-Marvik --- Mentor][2022 -- 2024][
  University of Utah, Nursing School, Ph.D. Health Sciences. Network science and social network analysis.]
#dated[Porter Bischoff --- Mentor, RA][Summer 2023][
  University of Utah + Utah Valley University, Summer Program for Undergraduate Research (SPUR).
  Network visualization using R.]
#dated[Luis Lopez --- Mentor][2022][NIH Postbac program. Exponential-family random graph models.]
```

# Conference Talks and Workshops

```{r}
#| results: asis
emit_section(talks, "conferencetalk", fmt_talk)
```

# Invited Talks

```{r}
#| results: asis
emit_section(talks, "invitedtalk", fmt_talk)
```

# Other Talks

```{r}
#| results: asis
emit_section(talks, "othertalk", fmt_talk)
```

# Honors and Services to the Profession

**Manuscript review (ad hoc).**
Journal of the American Statistical Association ·
American Sociological Review ·
Communications Physics ·
PLOS ONE ·
BMC Infectious Diseases ·
The Official Journal of the Society for Computational Economics ·
The R Journal ·
The Stata Journal ·
Social Networks ·
Journal of Mathematical Sociology ·
Computer Methods and Programs in Biomedicine Update ·
Journal of Open Source Software ·
Bioinformatics

**Abstract review.**
International Conference on Computational Social Science (2019--2021) ·
SUNBELT Conference (2016)

**Panelist / discussant.**
"Learning tips for your PhD from other researchers in the community,"
Early and Middle Career Researchers (EMCRs) on Social Networks workshops, October 2023 ·
"JASA A&CS Special Invited Session: A Tale of Two Datasets --- Representativeness and
Generalisability of Inference for Samples of Networks," Joint Statistical Meetings (JSM),
August 2023 ·
"Social Network Diffusion of Individual Behavior Change Interventions Virtual Workshop,"
National Institute on Aging, Division of Behavioral and Social Research, March 2022

**Book review.**
*Microeconometrics and Matlab: An Introduction*, by Adams, Clarke and Quinn,
Oxford University Press, 2015 ·
*Mastering Gephi Network Visualization*, by Ken Cherven, Packt Publishing, 2015 ·
*Network Graph Analysis and Visualization with Gephi*, by Ken Cherven, Packt Publishing, 2013

**Memberships and organizing.**
Core member, [University of Utah's Center for Data Science](https://datascience.utah.edu) (2023--Present) ·
Lead, [Network Science and Social Network Analysis at the U (NetSNAU)](https://netsci.utah.edu) (2022--Present) ·
Member, Center for Applied Network Analysis (CANA) at USC (2016--Present) ·
Co-organizer, [USC Networks Meeting](https://networkanalysis.usc.edu) (2020, 2021) ·
Founder, the first [R Users Group in Chile](https://www.meetup.com/useRchile/) (2013) ·
Co-organizer, [East LA R User Group](https://socalr.org)

# Technical Skills

R · C++ · Python · LaTeX · SQL · XML · regex · Stata+Mata · VBA · Gephi ·
Pajek · Mathematica · MS Office · Git · Unix · Docker · Visual Studio Code

```{r}
#| results: asis
cat(sprintf(paste0(
  "\n```{=typst}\n#v(1em)\n#align(center)[#text(size: 8pt, fill: muted)[",
  "last update: %s \\\n #link(\"https://ggvy.cl\")[ggvy.cl]]]\n```\n"),
  format(Sys.Date(), "%B %d, %Y")))
```
